### 2019-07-23 2_task_bench.tex
Tweak text and font sizes.
Shuffle figures around.
Add table of task bench parameters.
Edits for top of section 2.

To measure a wide variety of
systems and application scenarios, we developed a novel
parameterized benchmark called Task Bench. Task Bench
implementations execute a \emph{task graph}, with tasks for each point
in an \emph{iteration space} and dependencies between tasks determined
by a \emph{dependence relation}. A task $A$ that depends on another task $B$
must execute after task $B$, and receives the output data from
task $B$ as input. Each task can execute any one of a
number of kernels (compute-bound, memory-bound, etc.) and can generate
a configurable amount of output to control the amount of communication
performed with each task dependency. Thus Task Bench can explore a large space of application scenarios to
understand the performance of parallel and
distributed programming systems.

For simplicity, but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, column $i$ represents all tasks
with index $i$ in the iteration space over all the time
steps. Generally speaking each column will be
assigned to execute on a different processor core.

>>>>

\input{t2_parameters}

To explore as broad a space of application scenarios as possible, Task
Bench provides a large number of configuration parameters. The most
important parameters are described in
Table~\ref{tab:parameters}. These parameters control the size and
structure of the task graph, the type and duration of the kernels
associated with each task, and the amount of data associated with
each dependence edge in the graph.

Task graphs are a combination of an iteration space (with a task for
each point in the space) with a dependence relation.
For simplicity, but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, column $i$ represents all tasks
with index $i$ in the iteration space over all the time
steps. Generally speaking each column will be
assigned to execute on a different processor core.
